---
title: "EDS 212 Day 2 Part 1 - Derivatives & Git Intro"
author: "Ruth Enriquez"
date: "2022-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Derivatives in R - using dervi function on an expression

Find the derivative of $$f(x) = 5^2$$

```{r}
ex_1 <- expression(5 * x^2)

my_derivative <- deriv(ex_1, "x")
my_derivative

# I want to find the slope at x = 2.8

x <-2.8
eval(my_derivative)
```

## Finding derivatives using the "Capital D" method 
Find the slope of $g(z) = 2z^3-10.5z^2+4.1$

```{r}
gz <-expression(2 * z^3 - 10.5 * z^2 + 4.1)

dg_dz <-D(gz, 'z')
dg_dz
#can be single or double ' or "

#Let's evaluate the slope over a range of values
z <- seq(from = -3, to = 4, by = 0.5)

# Evaluate it!
eval(dg_dz)
```

#git is software built for version control for code, the workshorse tracking changes as you edit your data science project that you're working on

#github is an online plateform that makes it easier for us to manage that, PM, collab, view changes, and publishing

#using it together, they're not the same, there are other plateforms to work with, many of those are used to make git easier to use

#make this a version control project, going to use two functions and a package usethis:: in the console

#tracking git locally

hi