---
title: "EDS 212 Day 2 Part 1 - Derivatives & Git Intro"
author: "Ruth Enriquez"
date: "2022-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Derivatives in R - using dervi function on an expression

Find the derivative of $$f(x) = 5^2$$

```{r}
ex_1 <- expression(5 * x^2)

my_derivative <- deriv(ex_1, "x")
my_derivative

# I want to find the slope at x = 2.8

x <-2.8
eval(my_derivative)
```

## Finding derivatives using the "Capital D" method 
Find the slope of $g(z) = 2z^3-10.5z^2+4.1$

```{r}
gz <-expression(2 * z^3 - 10.5 * z^2 + 4.1)

dg_dz <-D(gz, 'z')
dg_dz
#can be single or double ' or "

#Let's evaluate the slope over a range of values
z <- seq(from = -3, to = 4, by = 0.5)

# Evaluate it!
eval(dg_dz)
```

#git is software built for version control for code, the workshorse tracking changes as you edit your data science project that you're working on

#github is an online plateform that makes it easier for us to manage that, PM, collab, view changes, and publishing

#using it together, they're not the same, there are other plateforms to work with, many of those are used to make git easier to use

#make this a version control project, going to use two functions and a package usethis:: in the console

#tracking git locally

#this only still exist on our computer but it is getting tracked
#going to connect this to a remote repository

some awesome text!!!

#before you save any changes you won't see any in the Git tab, as soon as you make changes, the file that has been changed will appear in the Git tab... with an M (M=modified)
#first level of security, hitting save, has saved it to the computer, next lvl of security (with a history) the first, staging, these are the things I am ready to "ship.
#>Select Stage >Press Commit >put commit message (on screen you can scroll down and show what was changed), no error, it uploaded
#push change = sending locally rep to the git hub repo, Press push

Another cool line!